\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-03-07 k-planar.tex
updates
Hmmmm

	Let $M$ and $M^+$ denote the subgraph of $G$ containing the edges and vertices of $\overline{Y}$, respectively $\overline{Y}^+$, and the edges and vertices of $F$.  By the choice of $\tau$, the vertices on the boundary of each inner face of $M$ are contained in $Y\cup P_a\cup P_b$ for some $a,b\in\{1,\ldots,k\}$.  In particular if $k=3$ then, for each inner face $f$ of $M$ there exists some $c\in\{1,2,3\}$ such that no vertex of $P_c$ is on the boundary of $f$.

>>>>

	Let $M$ and $M^+$ denote the subgraph of $G$ containing the edges and vertices of $\overline{Y}$, respectively $\overline{Y}^+$, and the edges and vertices of $F$. (See \cref{boring_figure}.)  By the choice of $\tau$, the vertices on the boundary of each inner face of $M$ are contained in $Y\cup P_a\cup P_b$ for some $a,b\in\{1,\ldots,k\}$.  In particular if $k=3$ then, for each inner face $F_i$ of $M$ there exists some $c\in\{1,2,3\}$ such that no vertex of $P_c$ is on the boundary of $F_i$.
